Abstraction and Invariance for Algebraically Indexed Types

### 2012-07-10 paper/paper.tex
POPL ICFP abbreviation

\bibitem{abadi99core} 
M. Abadi, A. Banerjee, N. Heintze, and J. G. Riecke. A Core Calculus
of Dependency. Proceedings, Symposium on Principles of Programming
Languages, pp.147-160, 1999.

@@

@@

\bibitem{chaudhuri10continuity}
S. Chaudhuri, S. Gulwani, and R. Lublinerman.  Continuity Analysis of
Programs.  Proceedings, Symposium on Principles of Programming
Languages, pp. 57-70, 2010.

\bibitem{gallier11geometric}
J. Gallier. {\em Geometric Methods and Applications, For Computer
Science and Engineering. Springer Science+Business Media, LLC}, 2011.

@@

\bibitem{kennedy97relational} 
A.~Kennedy. Relational Parametricity and Units of Measure.
Proceedings, Symposium on Principles of Programming Languages,
pp. 442-455, 1997.

@@

\bibitem{reed10distance}
J.~Reed and B.~C.~Pierce.  Distance Makes the Types Grow Stronger.
Proceedings, International Conference on Functional Programming,
pp. 157-169, 2010.

@@

\bibitem{sabelfeld01per} 
A.~Sabelfeld and D.~Sands.  A Per Model of Secure Information Flow in
Sequential Programs.  {\em Higher-Order and Symbolic Computation} 14
(1), pp. 59-91, 2001.

\bibitem{tse04translating}
S.~Tse and S.~Zdancewic.  Translating Dependency into Parametricity.
Proceedings, International Conference on Functional Programming pp.
115-125, 2004.

>>>>

\bibitem{abadi99core} 
M. Abadi, A. Banerjee, N. Heintze, and J. G. Riecke. A Core Calculus
of Dependency. Proceedings, POPL, pp.147-160, 1999.

@@

\bibitem{Cardelli}
L.~Cardelli, P.~Gardner.
Processes in Space.
{\em Programs, Proofs, Processes}: Proc, 6th Conference on Computability in Europe, pp 78-87, LNCS vol. 6158, 2010.

@@

\bibitem{chaudhuri10continuity}
S. Chaudhuri, S. Gulwani, and R. Lublinerman.  Continuity Analysis of
Programs.  Proceedings, POPL, pp. 57-70, 2010.

\bibitem{gallier11geometric}
J. Gallier. {\em Geometric Methods and Applications For Computer
Science and Engineering}. Springer, 2011.

@@

\bibitem{kennedy97relational} 
A.~Kennedy. Relational Parametricity and Units of Measure.
Proceedings, POPL, pp. 442-455, 1997.

@@

\bibitem{reed10distance}
J.~Reed and B.~C.~Pierce.  Distance Makes the Types Grow Stronger.
Proceedings, ICFP, pp. 157-169, 2010.

@@

\bibitem{sabelfeld01per} 
A.~Sabelfeld and D.~Sands.  A PER Model of Secure Information Flow in
Sequential Programs.  {\em Higher-Order and Symbolic Computation} 14
(1), pp. 59-91, 2001.

\bibitem{tse04translating}
S.~Tse and S.~Zdancewic.  Translating Dependency into Parametricity.
Proceedings, ICFP,  pp.
115-125, 2004.
